### 2016-06-23 docs/ms_communitySynchrony.Rmd
R1 version; sent to coauthors

Simulation experiments revealed that removing environmental fluctuations has the largest impact on synchrony, leading to a reduction in synchrony of species growth rates in four out of five communities (Fig. 1).
Removing environmental fluctuations ("No E.S" simulations) decreased synchrony by 33% in Arizona, 48% in Kansas, 39% in Montana, and 40% in New Mexico.
Only in Idaho did removing environmental fluctuations cause an increase in synchrony (Fig. 1), but the effect was small (9% increase; Table S2).
Overall, species' temporal random effects in the statistical vital rate models are positively correlated (Table S3).
Species interactions are weak in these communities [Table S4 and @Chu2015], and removing \hl{interspecific interactions} had little effect on synchrony (Fig. 1; "No Comp." simulations).
Removing competition caused, at most, a 5% change in synchrony (Fig. 1).
Removing demographic stochasticity ("No D.S." simulations) caused synchrony to increase slightly in all communities (Fig. 1), with an average 6% increase over synchrony from IBM simulations on a five meter area.

@@

### Simulations support theoretical predictions
Our theoretical predictions were derived from a simple model of population dynamics and required several simplifying assumptions, raising questions about their relevance to natural communities.
\hl{For example, the species in our communities do not have equivalent environmental and demographic variances (Figs. Sx-Sx), as required by our predictions.}
However, the theoretical predictions were strongly supported by simulations of population models fit to long-term data from natural plant communities (Table 3).
Such a close match between our analytical predictions and the simulation results should inspire confidence in the ability of simple models to inform our understanding of species synchrony, \hl{and allows us to place our simulation results within the context of contemporary theory}.

@@

In the Idaho community, removing environmental fluctuations did not cause a large decrease in synchrony.
However, that result appears to be an artifact. 
Removing environmental variation results in a negative invasion growth rate for *A. tripartita*. 
Although we only analyzed IBM runs in which *A. tripartita* had not yet gone extinct, it was at much lower abundance than in the other simulation runs.
When we removed *A. tripartita* from all simulations, the Idaho results conformed with results from all other sites: removing environmental stochasticity caused a significant reduction in species synchrony (Fig. S4).
Our main results for Idaho (Fig. 2), with *A. tripartita* included, demonstrate how the processes that determine species synchrony interact in complex ways.
*A. tripartita* has a facilitative effect on each grass species across all vital rates, except for a small competitive effect on *H. comata*'s survival probability (Tables S8-S10).
At the same time, all the perennial grasses have negative effects on each other for each vital rate (Tables S8-S10).
We know synchrony is affected by interspecific competition [@Loreau2008a], but how facilitative effects manifest themselves is unknown.
The interaction of facilitation and competition is clearly capable of having a large effect on species synchrony, and future theoretical efforts should aim to include a wider range of species interactions.

@@

\begin{figure}[!ht]
  \centering
      \includegraphics[width=4in]{./components/formatted_figures/formatted_figure3.png}
  \caption{Synchrony of species per capita growth rates when species are growing in isolation (IPM without species interactions) versus synchrony in polycultures (IPM with species interactions). We used the same sequence of random year effects for both simulations (with and without species interactions) to mimic biodiversity-ecosystem functioning experiments. The dashed line is the line of equality. Simulation results in this figure are analagous to ``No Comp. + No D.S.'' (species in isolation) and ``No D.S.'' (species in competition) in Fig. 1, but here we control the time series of random year effects.}
\end{figure}

>>>>

Simulation experiments revealed that removing environmental fluctuations has the largest impact on synchrony, leading to a reduction in synchrony of species growth rates in four out of five communities (Fig. 1).
Removing environmental fluctuations ("No E.S" simulations) decreased synchrony by 33% in Arizona, 48% in Kansas, 39% in Montana, and 40% in New Mexico.
Only in Idaho did removing environmental fluctuations cause an increase in synchrony (Fig. 1), but the effect was small (9% increase; Table S2).
Overall, species' temporal random effects in the statistical vital rate models are positively correlated (Table S3).
Species interactions are weak in these communities [Table S4 and @Chu2015], and removing \hl{interspecific interactions} had little effect on synchrony (Fig. 1; "No Comp." simulations).
Removing \hl{interspecific interactions} caused, at most, a 5% change in synchrony (Fig. 1).
Removing demographic stochasticity ("No D.S." simulations) caused synchrony to increase slightly in all communities (Fig. 1), with an average 6% increase over synchrony from IBM simulations on a five meter area.

@@

### Simulations support theoretical predictions
Our theoretical predictions were derived from a simple model of population dynamics and required several simplifying assumptions, raising questions about their relevance to natural communities.
\hl{For example, the species in our communities do not have equivalent environmental and demographic variances (Figs. S4-S7), as required by our predictions.}
However, the theoretical predictions were strongly supported by simulations of population models fit to long-term data from natural plant communities (Table 3).
Such a close match between our analytical predictions and the simulation results should inspire confidence in the ability of simple models to inform our understanding of species synchrony, \hl{and allows us to place our simulation results within the context of contemporary theory}.

@@

In the Idaho community, removing environmental fluctuations did not cause a large decrease in synchrony.
However, that result appears to be an artifact. 
Removing environmental variation results in a negative invasion growth rate for *A. tripartita*. 
Although we only analyzed IBM runs in which *A. tripartita* had not yet gone extinct, it was at much lower abundance than in the other simulation runs.
When we removed *A. tripartita* from all simulations, the Idaho results conformed with results from all other sites: removing environmental stochasticity caused a significant reduction in species synchrony (Fig. S8).
Our main results for Idaho (Fig. 2), with *A. tripartita* included, demonstrate how the processes that determine species synchrony interact in complex ways.
*A. tripartita* has a facilitative effect on each grass species across all vital rates, except for a small competitive effect on *H. comata*'s survival probability (Tables S8-S10).
At the same time, all the perennial grasses have negative effects on each other for each vital rate (Tables S8-S10).
We know synchrony is affected by interspecific competition [@Loreau2008a], but how facilitative effects manifest themselves is unknown.
The interaction of facilitation and competition is clearly capable of having a large effect on species synchrony, and future theoretical efforts should aim to include a wider range of species interactions.

@@

\begin{figure}[!ht]
  \centering
      \includegraphics[width=3in]{./components/formatted_figures/formatted_figure3.png}
  \caption{Synchrony of species per capita growth rates when species are growing in isolation (IPM without species interactions) versus synchrony in polycultures (IPM with species interactions). We used the same sequence of random year effects for both simulations (with and without species interactions) to mimic biodiversity-ecosystem functioning experiments. The dashed line is the line of equality. Simulation results in this figure are analagous to ``No Comp. + No D.S.'' (species in isolation) and ``No D.S.'' (species in competition) in Fig. 1, but here we control the time series of random year effects.}
\end{figure}

### 2016-06-23 docs/online_supporting_information.Rmd
R1 version; sent to coauthors

@@

\begin{figure}[!ht]
  \centering
      \includegraphics[width=6in]{./components/cv_vs_synchrony.png}
  \caption{Relationship between species synchrony (percent cover, top panels; growth rates, bottom panels) and the coefficient of variation of summed community cover. Each point represents a single time series from simulations and is color coded according to simulation experiment. Results from IBM simulations are from 25$\text{m}^2$ landscapes. Within experiments, the CV of total cover increases with synchrony of percent cover. The relationship between CV of total cover and synchrony of per capita growth rates within experiments is weaker. Among experiments, CV of total cover is lowest when the synchrony of per capita growth rates is lowest, confirming the link between species synchrony and ecosystem stability. Because our main focus is on species synchrony, we simply removed environmental variation rather than breaking the covariance structure of species environmental responses. Therefore, CV of total cover is drastically reduced when we remove environmental variation (``No E.S.'' points). However, regardless of environmental variance, CV of total cover is always reduced when synhrony is reduced.}
\end{figure}

@@

# Recruitment
vr_do <- vr_files[grep("recruit",vr_files)]
tmp_vital <- readRDS(paste0("../results/",vr_do))
names_vital <- readRDS(paste0("../results/",vr_files[1]))
sites <- names(tmp_vital)
mat_list <- list()
for(do_site in sites){
  tmp <- tmp_vital[[do_site]]
  spp <- names(names_vital[[do_site]])
  tmpdd <- tmp[grep("dd", rownames(tmp)),"Mean"]
  tmpmat <- matrix(tmpdd,length(spp),length(spp), byrow = FALSE)
  rownames(tmpmat) <- spp
  colnames(tmpmat) <- spp
  mat_list[[do_site]] <- tmpmat
}
vital_mat_list[["recruit"]] <- mat_list

>>>>

\begin{figure}[!ht]
  \centering
      \includegraphics[width=6in]{./components/formatted_figures/environmental_variances_cover.png}
  \caption{Variance of percent cover for each species (along x-axes) in each site through time from simulations with only environmental stochasticity operating (IPM with no species interactions).}
\end{figure}

\begin{figure}[!ht]
  \centering
      \includegraphics[width=6in]{./components/formatted_figures/environmental_variances_pgr.png}
  \caption{Variance of per capita growth rates for each species (along x-axes) in each site through time from simulations with only environmental stochasticity operating (IPM with no species interactions).}
\end{figure}

\begin{figure}[!ht]
  \centering
      \includegraphics[width=6in]{./components/formatted_figures/demographic_variances_cover.png}
  \caption{Variance of percent cover for each species (along x-axes) in each site through time from simulations with only demographic stochasticity operating (IBM simulated on 5 by 5 meter landscape).}
\end{figure}

\begin{figure}[!ht]
  \centering
      \includegraphics[width=6in]{./components/formatted_figures/demographic_variances_pgr.png}
  \caption{Variance of per capita growth rates for each species (along x-axes) in each site through time from simulations with only demographic stochasticity operating (IBM simulated on 5 by 5 meter landscape).}
\end{figure}

@@

<!---
\begin{figure}[!ht]
  \centering
      \includegraphics[width=6in]{./components/cv_vs_synchrony.png}
  \caption{Relationship between species synchrony (percent cover, top panels; growth rates, bottom panels) and the coefficient of variation of summed community cover. Each point represents a single time series from simulations and is color coded according to simulation experiment. Results from IBM simulations are from 25$\text{m}^2$ landscapes. Within experiments, the CV of total cover increases with synchrony of percent cover. The relationship between CV of total cover and synchrony of per capita growth rates within experiments is weaker. Among experiments, CV of total cover is lowest when the synchrony of per capita growth rates is lowest, confirming the link between species synchrony and ecosystem stability. Because our main focus is on species synchrony, we simply removed environmental variation rather than breaking the covariance structure of species environmental responses. Therefore, CV of total cover is drastically reduced when we remove environmental variation (``No E.S.'' points). However, regardless of environmental variance, CV of total cover is always reduced when synhrony is reduced.}
\end{figure}

\newpage{}
--->

@@

####
####  Loop Over Files and Extract Crowding Effects -----------------------------
####
# Growth and survival first
vital_mat_list <- list()
for(do_vital in vital_rates[c(1,2)]){
  vr_do <- vr_files[grep(do_vital,vr_files)]
  torms <- grep("yr", vr_do)
  vr_do <- vr_do[-torms]
  tmp_vital <- readRDS(paste0("../results/",vr_do))
  sites <- names(tmp_vital)
  mat_list <- list()
  for(do_site in sites){
    tmp <- tmp_vital[[do_site]]
    spp <- names(tmp)
    tmpmat <- matrix(0,nrow = length(spp), ncol = length(spp))
    for(i in 1:length(spp)){
      do_spp <- spp[i]
      tmpspp <- tmp[[do_spp]]
      tmpw <- tmpspp[1,grep("crowd*", colnames(tmpspp))]
      tmpmat[i,] <- as.numeric(tmpw)
    }
    rownames(tmpmat) <- spp
    colnames(tmpmat) <- spp
    mat_list[[do_site]] <- tmpmat
  }
  vital_mat_list[[do_vital]] <- mat_list 
}

# Recruitment
vr_do <- vr_files[grep("recruit",vr_files)]
torms <- c(grep("yr", vr_do), grep("MONT", vr_do))
vr_do <- vr_do[-torms]
tmp_vital <- readRDS(paste0("../results/",vr_do))
names_vital <- readRDS(paste0("../results/",vr_files[1]))
sites <- names(tmp_vital)
mat_list <- list()
for(do_site in sites){
  tmp <- tmp_vital[[do_site]]
  spp <- names(names_vital[[do_site]])
  tmpdd <- tmp[grep("dd", rownames(tmp)),"Mean"]
  tmpmat <- matrix(tmpdd,length(spp),length(spp), byrow = FALSE)
  rownames(tmpmat) <- spp
  colnames(tmpmat) <- spp
  mat_list[[do_site]] <- tmpmat
}
vital_mat_list[["recruit"]] <- mat_list

### 2016-06-23 docs/online_supporting_information.tex
R1 version; sent to coauthors

\begin{figure}[!ht]
  \centering
      \includegraphics[width=6in]{./components/cv_vs_synchrony.png}
  \caption{Relationship between species synchrony (percent cover, top panels; growth rates, bottom panels) and the coefficient of variation of summed community cover. Each point represents a single time series from simulations and is color coded according to simulation experiment. Results from IBM simulations are from 25$\text{m}^2$ landscapes. Within experiments, the CV of total cover increases with synchrony of percent cover. The relationship between CV of total cover and synchrony of per capita growth rates within experiments is weaker. Among experiments, CV of total cover is lowest when the synchrony of per capita growth rates is lowest, confirming the link between species synchrony and ecosystem stability. Because our main focus is on species synchrony, we simply removed environmental variation rather than breaking the covariance structure of species environmental responses. Therefore, CV of total cover is drastically reduced when we remove environmental variation (``No E.S.'' points). However, regardless of environmental variance, CV of total cover is always reduced when synhrony is reduced.}
\end{figure}

@@

\begin{table}[ht]
\centering
\caption{Comparisons between our analytical predictions and simulation results for synchrony of species' per capita growth rates. Analytical predictions represent two limiting cases where only demographic stochasticity is operating ($\phi_{R,\mathcal{M}_D}$) and where only environmental stochasticity is operating ($\phi_{R,\mathcal{M}_E}$). Simulated synchrony values come from our empirically-based, multi-species population models when simulated under conditions that match the limiting case conditions (e.g., environmental stochasticity and competition removed for $\mathcal{M}_D$).} 
{\normalsize
\begin{tabular}{lrrrr}
  \hline
Site & Predicted $\phi_{R,\mathcal{M}_D}$ & Simulated $\phi_{R,\mathcal{M}_D}$ & Predicted $\phi_{R,\mathcal{M}_E}$ & Simulated $\phi_{R,\mathcal{M}_E}$ \\ 
  \hline
New Mexico & 0.56 & 0.51 & 0.86 & 0.86 \\ 
  Arizona & 0.51 & 0.52 & 0.82 & 0.82 \\ 
  Kansas & 0.35 & 0.39 & 0.62 & 0.62 \\ 
  Montana & 0.31 & 0.33 & 0.47 & 0.49 \\ 
  Idaho & 0.29 & 0.31 & 0.43 & 0.41 \\ 
   \hline
\end{tabular}
}
\end{table}

\begin{table}[ht]
\centering
\caption{Percent differences of synchrony of per capita growth rates between each removal simulation experiment and the 'All Drivers' simulation.} 
\begin{tabular}{lrrrrr}
  \hline
simulation & 1New Mexico & 2Arizona & 3Kansas & 4Montana & 5Idaho \\ 
  \hline
1No D.S. & 4.82 & 3.99 & 7.19 & 5.37 & 9.53 \\ 
  2No Comp. + No D.S. & 4.74 & 2.70 & 6.81 & 4.53 & 7.69 \\ 
  4No Comp. & 0.98 & 0.06 & 4.84 & 1.01 & 0.11 \\ 
  5No E.S. & 40.14 & 33.20 & 47.84 & 38.52 & 9.28 \\ 
  6No Comp. + No E.S. & 45.95 & 41.48 & 38.21 & 33.07 & 20.33 \\ 
   \hline
\end{tabular}
\end{table}

\begin{table}[ht]
\centering
\caption{Correlations of species' year random effects for each site by term, where term refers to the random effect on the slope or the intercept.} 
\begin{tabular}{llrrr}
  \hline
site & term & growth & recruit & surv \\ 
  \hline
Arizona & intercept & 0.49 & -0.05 & 0.45 \\ 
  Arizona & slope & 0.68 &  & 0.15 \\ 
  Idaho & intercept & 0.46 & 0.38 & 0.29 \\ 
  Idaho & slope & 0.50 &  & 0.47 \\ 
  Kansas & intercept & 0.47 & 0.29 & 0.24 \\ 
  Kansas & slope & 0.18 &  & 0.16 \\ 
  Montana & intercept & 0.26 & 0.04 & 0.39 \\ 
  Montana & slope & 0.10 &  & 0.01 \\ 
  NewMexico & intercept & 0.54 & -0.15 & 0.64 \\ 
  NewMexico & slope & 0.32 &  & 0.15 \\ 
   \hline
\end{tabular}
\end{table}

\begin{table}[ht]
\centering
\caption{Average interaction coefficients for each vital rate for each community.} 
\begin{tabular}{llrrr}
  \hline
Site & Interaction Type & Growth & Recruitment & Survival \\ 
  \hline
Arizona & Interspecific & -0.0111 & -0.4534 & -0.0507 \\ 
  Arizona & Intraspecific & -0.0402 & -1.4209 & -0.4446 \\ 
  Idaho & Interspecific & 0.0022 & -0.1091 & 0.0059 \\ 
  Idaho & Intraspecific & -0.0469 & -1.5569 & -0.5269 \\ 
  Kansas & Interspecific & -0.0008 & 0.0463 & -0.0041 \\ 
  Kansas & Intraspecific & -0.0062 & -0.9945 & -0.0586 \\ 
  Montana & Interspecific & -0.0053 & 0.0920 & 0.0354 \\ 
  Montana & Intraspecific & -0.0733 & -2.0492 & -0.8103 \\ 
  NewMexico & Interspecific & -0.0027 & -0.3461 & -0.0080 \\ 
  NewMexico & Intraspecific & -0.0111 & -1.6473 & -0.2191 \\ 
   \hline
\end{tabular}
\end{table}

>>>>

@@

\begin{table}[ht]
\centering
\caption{Comparisons between our analytical predictions and simulation results for synchrony of species' per capita growth rates. Analytical predictions represent two limiting cases where only demographic stochasticity is operating ($\phi_{R,\mathcal{M}_D}$) and where only environmental stochasticity is operating ($\phi_{R,\mathcal{M}_E}$). Simulated synchrony values come from our empirically-based, multi-species population models when simulated under conditions that match the limiting case conditions (e.g., environmental stochasticity and competition removed for $\mathcal{M}_D$).} 
{\normalsize
\begin{tabular}{lrrrr}
  \hline
Site & Predicted $\phi_{R,\mathcal{M}_D}$ & Simulated $\phi_{R,\mathcal{M}_D}$ & Predicted $\phi_{R,\mathcal{M}_E}$ & Simulated $\phi_{R,\mathcal{M}_E}$ \\ 
  \hline
New Mexico & 0.56 & 0.51 & 0.86 & 0.86 \\ 
  Arizona & 0.51 & 0.52 & 0.82 & 0.81 \\ 
  Kansas & 0.35 & 0.39 & 0.62 & 0.62 \\ 
  Montana & 0.31 & 0.31 & 0.47 & 0.50 \\ 
  Idaho & 0.29 & 0.31 & 0.43 & 0.42 \\ 
   \hline
\end{tabular}
}
\end{table}

\begin{table}[ht]
\centering
\caption{Percent differences of synchrony of per capita growth rates between each removal simulation experiment and the 'All Drivers' simulation.} 
\begin{tabular}{lrrrrr}
  \hline
simulation & 1New Mexico & 2Arizona & 3Kansas & 4Montana & 5Idaho \\ 
  \hline
1No D.S. & 5.53 & 4.28 & 6.01 & 5.27 & 11.95 \\ 
  2No Comp. + No D.S. & 5.56 & 2.06 & 7.03 & 6.21 & 9.10 \\ 
  4No Comp. & 0.98 & 0.06 & 4.84 & 1.43 & 0.11 \\ 
  5No E.S. & 40.14 & 33.20 & 47.84 & 39.06 & 9.28 \\ 
  6No Comp. + No E.S. & 45.95 & 41.48 & 38.21 & 39.44 & 20.33 \\ 
   \hline
\end{tabular}
\end{table}

\begin{table}[ht]
\centering
\caption{Correlations of species' year random effects for each site by term, where term refers to the random effect on the slope or the intercept.} 
\begin{tabular}{llrrr}
  \hline
site & term & growth & recruit & surv \\ 
  \hline
Arizona & intercept & 0.51 & -0.05 & 0.51 \\ 
  Arizona & slope & 0.68 &  & 0.16 \\ 
  Idaho & intercept & 0.45 & 0.38 & 0.25 \\ 
  Idaho & slope & 0.50 &  & 0.47 \\ 
  Kansas & intercept & 0.44 & 0.29 & 0.26 \\ 
  Kansas & slope & 0.19 &  & 0.16 \\ 
  Montana & intercept & 0.29 & 0.07 & 0.41 \\ 
  Montana & slope & 0.11 &  & 0.02 \\ 
  NewMexico & intercept & 0.51 & -0.15 & 0.65 \\ 
  NewMexico & slope & 0.37 &  & 0.20 \\ 
   \hline
\end{tabular}
\end{table}

\begin{table}[ht]
\centering
\caption{Average interaction coefficients for each vital rate for each community.} 
\begin{tabular}{llrrr}
  \hline
Site & Interaction Type & Growth & Recruitment & Survival \\ 
  \hline
Arizona & Interspecific & -0.0111 & -0.4534 & -0.0507 \\ 
  Arizona & Intraspecific & -0.0402 & -1.4209 & -0.4446 \\ 
  Idaho & Interspecific & 0.0022 & -0.1091 & 0.0059 \\ 
  Idaho & Intraspecific & -0.0469 & -1.5569 & -0.5269 \\ 
  Kansas & Interspecific & -0.0008 & 0.0463 & -0.0041 \\ 
  Kansas & Intraspecific & -0.0062 & -0.9945 & -0.0586 \\ 
  Montana & Interspecific & -0.0059 & 0.0691 & 0.0342 \\ 
  Montana & Intraspecific & -0.0801 & -2.0900 & -0.8652 \\ 
  NewMexico & Interspecific & -0.0027 & -0.3461 & -0.0080 \\ 
  NewMexico & Intraspecific & -0.0111 & -1.6473 & -0.2191 \\ 
   \hline
\end{tabular}
\end{table}
